Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Enhancing deep learning-based CSI feedback in noisy channels with a soft variational approach

@@

>>>>

\cite{wang2024variational}Proposes a variational autoencoder framework for noisy-channel CSI feedback, formulating it as rate-distortion optimization. The method achieves 40\% bandwidth reduction versus \cite{abe} while maintaining NMSE robustness across SNRs, addressing limitations of uniform bit treatment in \cite{abn,chen2024transnet}.

@@

	\bibitem{wang2024variational}
	Y. Wang et al., ``Enhancing deep learning-based CSI feedback in noisy channels with a soft variational approach,'' \textit{IEEE Trans. Wireless Commun.}, early access, 2024.
